PANCHANGE_data_merging

### 2020-08-17 PANCHANGE_data_merging.Rmd
changes to merging script

# Import data
```{r export data}
glad <- read_rds(path = paste0(data_path, "/glad.rds"))

edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))

nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))

ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
```

glad/edgi data frame list
```{r glad/edgi data frame list}
dfs.list <- list(
  glad,
  edgi,
  nbr,
  ramp
)
```

```{r Join all questionnaires}
dat <- plyr::join_all(
  dfs.list,
  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
  )

#look at the data
skimr::skim(dat)
```

>>>>

# Import data
```{r export data}
glad <- read_rds(path = paste0(data_path, "/glad.rds"))
dim(glad)

edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
dim(edgi)

nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
dim(nbr)

ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
dim(ramp)
```

glad/edgi data frame list
```{r glad/edgi data frame list}
dat <- bind_rows(
  glad,
  edgi,
  nbr,
  ramp
)
```

```{r Skim data}
#look at the data
skimr::skim(dat)
```
